## Visual Analysis of Elon Musk's Tweets
#### By [Devin Didericksen](http://linkedin.com/in/didericksen) on October 11, 2014

```{r prep, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE}
library(dplyr)
library(rCharts)
library(ggplot2)
library(lubridate)
library(scales)
library(zoo)
#import data
setwd("/home/devin/R/data")
tweets <- read.csv("musk.csv", header = TRUE)
tweets <- tweets[tweets$reply == FALSE,c(-1,-5)]
tweets <- tweets[-dim(tweets)[1],]
tweets$text <- as.character(tweets$text)
tweets$created_at <- as.Date(tweets$created_at,format="%m/%d/%Y")
tweets$Topic <- as.character(tweets$topic)
tweets$Topic[tweets$topic == "t"] <- "Tesla"
tweets$Topic[tweets$topic == "x"] <- "SpaceX"
tweets$Topic[tweets$topic == "s"] <- "SolarCity"
tweets$Topic[tweets$topic == ""] <- "Other"
tweets$Topic <- factor(tweets$Topic, levels = c("Tesla","SpaceX","SolarCity","Other"))
tweets$Month <- floor_date(tweets$created_at, "month")
tweets2 <- summarise(group_by(tweets, Month, Topic),Count=n())
tweets$Quarter <- as.Date(as.yearqtr(tweets$created_at))
month(tweets$Quarter) <- month(tweets$Quarter) + 2
tweets3 <- summarise(group_by(tweets, Quarter, Topic),Count=n())
tweets3 <- tweets3[tweets3$Quarter > as.Date("2012-01-01"),]
#NVD3 does not like holes in data so we need to fill in the holes with NA's
dummy1 <- expand.grid(Topic = levels(tweets3$Topic), Quarter = levels(as.factor(tweets3$Quarter)))
dummy1$Quarter <- as.Date(dummy1$Quarter,format="%Y-%m-%d")
tweets4 <- left_join(dummy1,tweets3)
tweets4$Quarter <- as.factor(c(rep("Q1 2012",4),rep("Q2 2012",4),rep("Q3 2012",4),rep("Q4 2012",4),rep("Q1 2013",4),rep("Q2 2013",4),rep("Q3 2013",4),rep("Q4 2013",4),rep("Q1 2014",4),rep("Q2 2014",4),rep("Q3 2014",4)))
```

### Count of Tweets by Elon Musk Grouped by Topic

```{r nvd3, echo = FALSE, results ='asis', warning = FALSE, fig.width = 10}
n1 <- nPlot(Count ~ Quarter, group = "Topic", data = tweets4, type = "multiBarChart")
n1$xAxis(rotateLabels=-45)
n1$chart(reduceXTicks = FALSE,stacked=TRUE)
n1$print("chart3", include_assets=TRUE, cdn=TRUE)
```

### Charting the Data
To get the data I used the Twitter API and the python script [tweet_dumper.py](https://gist.github.com/yanofsky/5436496) to pull all of Elon's tweets. I only used tweets and retweets (no replies or favorites). I then categorized them based on their content into "Tesla", "SpaceX", "SolarCity", and "Other". Most of his tweets and retweets are directly related to one of his three companies. Of the "Other" tweets, most are about climate change (which incidentally is a driving influence for his involvement in all three companies). 

To create the charts I used R with the following packages: rCharts, ggplot2, dplyr, lubridate, scales, and zoo. The interactive chart above is part of the reusable chart library for D3 called NVD3. Below is the same chart, but static, using the ggplot2 library. My R code can be found [here](https://github.com/didericksen/musk-tweets/blob/gh-pages/musk.Rmd).

Special thanks to Ramnath Vaidyanathan, Hadley Wickham, and Yihui Xie for their R packages, and to Novus Partners for NVD3.

```{r ggplot, echo = FALSE, results ='asis', warning = FALSE, fig.width = 10}
ggplot(tweets3, aes(x = Quarter, y = Count, fill = Topic)) + stat_summary(fun.y = identity, geom = "bar", position = "stack") + scale_fill_brewer(palette = "Set1") + scale_x_date(breaks = seq(as.Date("2012-03-01"),as.Date("2014-09-01"),by="3 months"), labels = date_format("%b-%y"), limits = as.Date(c("2012-02-01","2014-10-01"))) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Tweets by Elon Musk Grouped by Topic")
```